---
title: "Design notes: Homage system"
name: design-notes
description: "Visual tokens, palette families, and component rules for albersdown."
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
params:
  family: "violet"     # red, lapis, ochre, teal, green, violet
  base_size: 13
  content_width: 80
vignette: >
  %\VignetteIndexEntry{Design notes: Homage system}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
css: albers.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.align = "center", fig.retina = 2,
  out.width = "100%", fig.width = 7, fig.asp = 0.618, message = FALSE, warning = FALSE
)
set.seed(123); options(pillar.sigfig = 7, width = 80)
library(ggplot2)
if (requireNamespace("albersdown", quietly = TRUE)) {
  theme_set(albersdown::theme_albers(params$family, base_size = params$base_size))
}
```

```{r albers-family, echo=FALSE, results='asis'}
cat(sprintf('<script>document.addEventListener("DOMContentLoaded",function(){document.body.classList.add("palette-%s");});</script>', params$family))
```

```{r content-width, echo=FALSE, results='asis'}
cat(sprintf('<style>:root{--content:%sch}</style>', params$content_width))
```

<div class="homage-hero" aria-hidden="true"></div>
<div class="hr-notch" role="presentation"></div>

## Overview {.overview}

- One family per page (A900/A700/A500/A300 → roles)
- Links + focus use AA tones; anchors show ▣ on hover
- Callouts and tables use quiet A300 tints; code blocks are flat with a small corner square

## Palette families and roles {#palettes}

Families available: red, lapis, ochre, teal, green, violet. Each has four tones:

- A900: links and focus in light mode; strongest contrast
- A700: highlights (one series per plot); nav active marker
- A500: borders, anchors (▣), code-corner square, hr notch
- A300: tints for callouts and table stripe; links/focus in dark mode

## Links, anchors, and rhythm {#links-anchors}

Links and focus rings always meet AA. Move the cursor over H2/H3 to reveal the square anchor glyph ▣.

<div class="hr-notch" role="presentation"></div>

## Callouts and code blocks {#callouts-code}

> TIP: Callouts use an A500 border and a subtle A300 tint (≈8–10%). Keep them short and purposeful.

```r
# a small, readable function
foo <- function(x) if (length(x) == 0) NA_real_ else mean(x)
foo(c(1, 2, 3))
```

The code fence has no drop shadow and includes a small A500 square in the top-left corner—a minimal homage.

## Tables {#tables}

Base HTML tables pick up a quiet A300 zebra stripe and thin borders.

```{r}
head(mtcars[, 1:5])
```

## Plots: one highlight, others neutral {#plots}

```{r}
mtcars$grp <- ifelse(mtcars$cyl == 6, "highlight", "other")
mtcars$grp <- factor(mtcars$grp, levels = c("other", "highlight"))
ggplot(mtcars, aes(wt, mpg, color = grp)) +
  geom_point(size = 2.2) +
  albersdown::scale_color_albers_highlight(
    family = params$family,
    tone = "A700",
    highlight = "highlight",
    other_name = "other"
  ) +
  labs(title = "One highlighted series; others neutral",
       subtitle = "A700 draws the eye; gray recedes",
       x = "Weight (1000 lbs)", y = "MPG")
```

## See also {#see-also}

<div class="hr-notch" role="presentation"></div>

- Getting started: `articles/getting-started.html`
- pkgdown template docs: `reference/index.html`
- Palette and roles: `#palettes`
