---
title: 'Design notes: Homage system'
name: design-notes
description: Visual tokens, palette families, and component rules for albersdown.
output:
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 2
    df_print: kable
params:
  family: violet
  preset: midnight
  base_size: 13
  content_width: 80
  style: minimal
vignette: |
  %\VignetteIndexEntry{Design notes: Homage system} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
css: albers.css
resource_files:
- albers.css
- albers.js
includes:
  in_header: |-
    <script src="albers.js"></script>
    <script>document.addEventListener('DOMContentLoaded',function(){document.body.classList.add('palette-lapis','preset-midnight');});</script>

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.align = "center", fig.retina = 2,
  out.width = "100%", fig.width = 7, fig.asp = 0.618, message = FALSE, warning = FALSE
)
set.seed(123); options(pillar.sigfig = 7, width = 80)
`%||%` <- function(a, b) if (is.null(a)) b else a
library(ggplot2)
if (requireNamespace("ggplot2", quietly = TRUE) && requireNamespace("albersdown", quietly = TRUE)) {
  ggplot2::theme_set(albersdown::theme_albers(params$family, base_size = params$base_size))
}
```

```{r albers-family, echo=FALSE, results='asis'}
cat(sprintf('<script>document.addEventListener("DOMContentLoaded",function(){document.body.classList.add("palette-%s");});</script>', params$family))
```

```{r albers-style, echo=FALSE, results='asis'}
style_class <- switch(
  tolower(params$style %||% "balanced"),
  minimal = "style-minimal",
  assertive = "style-assertive",
  balanced = ""
)
if (nzchar(style_class)) {
  cat(sprintf('<script>document.addEventListener("DOMContentLoaded",function(){document.body.classList.remove("style-minimal","style-assertive");document.body.classList.add("%s");});</script>', style_class))
}
```

```{r content-width, echo=FALSE, results='asis'}
cat(sprintf('<style>:root{--content:%sch}</style>', params$content_width))
```

<div class="homage-hero" aria-hidden="true"></div>
<div class="hr-notch" role="presentation"></div>

## Overview {.overview}

- One family per page (A900/A700/A500/A300 → roles)
- Links + focus use AA tones; anchors reveal a typographic dash on hover
- Callouts and tables use quiet A300 tints; code blocks use a structural left ribbon

## Palette families and roles {#palettes}

Families available: red, lapis, ochre, teal, green, violet. Each has four tones:

- A900: links and focus in light mode; strongest contrast
- A700: highlights (one series per plot); nav active marker
- A500: borders, dash anchors, code ribbons, structural rules
- A300: tints for callouts and table stripe; links/focus in dark mode

## Image-derived palettes {#image-palettes}

The original Homage families favor a single hue family per plot or page. When you want a different aesthetic (pulled from the grid image), use the image-derived palettes and scales. They mirror the API and are fully opt-in.

Sequential (image-based)

```{r img-seq, fig.height=3.2}
mtcars |>
  ggplot(aes(wt, mpg, colour = hp)) +
  geom_point(size = 2.2) +
  labs(title = "Image-derived sequential (lapis)") +
  albersdown::scale_color_albers_img("lapis", discrete = FALSE)
```

Diverging (image-based)

```{r img-div, fig.height=3.2}
df <- transform(datasets::faithful, centered = waiting - mean(waiting))
ggplot(df, aes(eruptions, centered, colour = centered)) +
  geom_point(alpha = 0.9) +
  labs(title = "Image-derived diverging (red <-> teal)") +
  albersdown::scale_color_albers_img_red_teal(neutral = "#e5e7eb")
```

Notes
- The `*_img` scales are opt-in and don’t change existing defaults.
- `neutral` can be set to `"#e5e7eb"` (site border token) for visual coherence with pages.
- Prefer the original single-family scales for a quieter, unified look; reach for the image-derived or diverging scales to emphasize contrasts.

## Links, anchors, and rhythm {#links-anchors}

Links and focus rings always meet AA. Move the cursor over H2/H3 to reveal the structural dash anchor.

Style modes
- `style: minimal` (default): lighter rules and quieter dash language.
- `style: balanced`: the calibrated middle ground.
- `style: assertive`: stronger edges and more emphatic structural marks.

<div class="hr-notch" role="presentation"></div>

## Callouts and code blocks {#callouts-code}

> TIP: Callouts use an A500 border and a subtle A300 tint (≈8–10%). Keep them short and purposeful.

```r
# a small, readable function
foo <- function(x) if (length(x) == 0) NA_real_ else mean(x)
foo(c(1, 2, 3))
```

The code fence stays flat: no drop shadow, with an A500 left ribbon and a compact copy control.

## Tables {#tables}

Base HTML tables pick up a quiet A300 zebra stripe and thin borders.

```{r}
knitr::kable(head(mtcars[, 1:5]), format = "html")
```

## Plots: one highlight, others neutral {#plots}

```{r}
mtcars$grp <- ifelse(mtcars$cyl == 6, "highlight", "other")
mtcars$grp <- factor(mtcars$grp, levels = c("other", "highlight"))
ggplot(mtcars, aes(wt, mpg, color = grp)) +
  geom_point(size = 2.2) +
  albersdown::scale_color_albers_highlight(
    family = params$family,
    tone = "A700",
    highlight = "highlight",
    other_name = "other"
  ) +
  labs(title = "One highlighted series; others neutral",
       subtitle = "A700 draws the eye; gray recedes",
       x = "Weight (1000 lbs)", y = "MPG")
```

## See also {#see-also}

<div class="hr-notch" role="presentation"></div>

- Getting started: `articles/getting-started.html`
- pkgdown template docs: `reference/index.html`
- Palette and roles: `#palettes`
