---
title: "Interaction: the cool direction"
name: interaction
description: The cool, grotesk, dark-code direction of the albersdown 2.0 theme.
output:
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 2
    css: albers.css
    includes:
      in_header: albers-header.html
params:
  family: lapis
  preset: interaction
resource_files:
- albers.css
- albers.js
- albers-header.html

vignette: |
  %\VignetteIndexEntry{Interaction: the cool direction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.align = "center", fig.retina = 2,
  out.width = "100%", fig.width = 7, fig.asp = 0.6, message = FALSE, warning = FALSE
)
set.seed(123)
oldopt <- options(pillar.sigfig = 7, width = 80)
library(ggplot2)
if (requireNamespace("ragg", quietly = TRUE)) knitr::opts_chunk$set(dev = "ragg_png")
if (requireNamespace("systemfonts", quietly = TRUE)) albersdown::albers_register_fonts()
if (requireNamespace("ggplot2", quietly = TRUE) && requireNamespace("albersdown", quietly = TRUE)) {
  ggplot2::theme_set(albersdown::theme_albers(family = params$family, preset = params$preset))
}
```

```{r albers-classes, echo=FALSE, results='asis'}
cat(sprintf(
  paste0(
    '<script>document.addEventListener("DOMContentLoaded",function(){',
    'document.body.classList.remove("palette-red","palette-lapis","palette-ochre","palette-teal","palette-green","palette-violet","preset-homage","preset-interaction","preset-study","preset-structural","preset-adobe","preset-midnight");',
    'document.body.classList.add("palette-%s","preset-%s");',
    '});</script>'
  ),
  params$family,
  params$preset
))
```

## Overview

This vignette is rendered in the **Interaction** direction: a cool grey ground,
all-grotesk type (Space Grotesk for display, Hanken Grotesk for body), and dark
code blocks. It is the counterpart to the warm, serif **Homage** direction shown
in `vignette("getting-started")`. Switching is a one-line change --
`preset: interaction` in the vignette YAML, or `theme_albers(preset =
"interaction")` for plots.

### How the two directions relate

A *direction* sets the ground, the type pairing, the code theme, and the
nested-square marker's outer ring. The *family* (here `lapis`) still drives the
accent: links, the marker's inner squares, and the plot palette all follow it.

## Dark code blocks

Code is rendered on a dark panel with light syntax tokens, while inline code
like `neighbor_graph()` stays a light chip so it reads inside body text.

```{r}
m <- matrix(rnorm(40), 8, 5)
round(cor(m), 2)
```

> TIP: The dark code block is part of the Interaction direction. In Homage the
> same block is a light cream panel -- the syntax colours adapt to stay legible
> on either ground.

## Tables

```{r}
knitr::kable(head(mtcars[, c("mpg", "wt", "hp", "cyl")]), caption = "A small table on the cool ground.")
```

## A plot on the matching ground

The plot's background is the same cool grey as the page, so the figure sits
seamlessly in the article rather than floating on a mismatched panel.

```{r}
mtcars |>
  ggplot(aes(wt, mpg, color = factor(cyl))) +
  geom_point(size = 2.4) +
  albersdown::scale_color_albers(family = params$family) +
  labs(
    title = "Fuel efficiency vs. weight",
    subtitle = "Interaction direction (cool) with the lapis family",
    x = "Weight (1000 lbs)", y = "MPG", color = "Cylinders"
  )
```

```{r cleanup, include=FALSE}
options(oldopt)
```
