---
title: 'Theme Proof: Ochre + Structural'
name: proof-ochre-structural
description: Full-page proof vignette for the ochre family on the structural preset.
output:
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 2
    css: albers.css
    includes:
      in_header: albers-header.html
params:
  family: ochre
  preset: structural
  base_size: 13
  content_width: 74
  style: minimal
vignette: |
  %\VignetteIndexEntry{Theme Proof: Ochre + Structural}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
resource_files:
- albers.css
- albers.js
- albers-header.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.align = "center", fig.retina = 2,
  out.width = "100%", fig.width = 7, fig.asp = 0.618, message = FALSE, warning = FALSE
)
set.seed(11)
oldopt <- options(pillar.sigfig = 7, width = 80)
`%||%` <- function(a, b) if (is.null(a)) b else a
library(ggplot2)
if (requireNamespace("ggplot2", quietly = TRUE) && requireNamespace("albersdown", quietly = TRUE)) {
  oldtheme <- ggplot2::theme_set(albersdown::theme_albers(
    family = params$family,
    preset = params$preset,
    base_size = params$base_size
  ))
}
```

```{r albers-family, echo=FALSE, results='asis'}
cat(sprintf('<script>document.addEventListener("DOMContentLoaded",function(){document.body.classList.add("palette-%s");});</script>', params$family))
```

```{r albers-preset, echo=FALSE, results='asis'}
cat(sprintf('<script>document.addEventListener("DOMContentLoaded",function(){document.body.classList.add("preset-%s");});</script>', params$preset))
```

```{r albers-style, echo=FALSE, results='asis'}
style_class <- switch(
  tolower(params$style %||% "balanced"),
  minimal = "style-minimal",
  assertive = "style-assertive",
  balanced = ""
)
if (nzchar(style_class)) {
  cat(sprintf('<script>document.addEventListener("DOMContentLoaded",function(){document.body.classList.remove("style-minimal","style-assertive");document.body.classList.add("%s");});</script>', style_class))
}
```

```{r content-width, echo=FALSE, results='asis'}
cat(sprintf('<style>:root{--content:%sch}</style>', params$content_width))
```

<div class="homage-hero" aria-hidden="true"></div>
<div class="hr-notch" role="presentation"></div>

## What To Look For

This proof page fixes the article to `ochre` plus `structural`.
The family should show up in links, section dividers, plot highlights, and emphasis bands.

The preset should feel more architectural than `study`: harder surfaces, flatter shadows,
and a drier ground color behind the same typography and layout system.

## Palette Evidence

```{r}
albersdown::albers_swatch(families = params$family, show_presets = TRUE) +
  ggplot2::labs(
    title = "Ochre palette tones with preset row",
    subtitle = "A second full-page combination so users can compare fixed articles directly"
  ) +
  ggplot2::theme(legend.position = "none")
```

## Plot Evidence

```{r}
counts <- as.data.frame(table(mtcars$cyl))
names(counts) <- c("cyl", "n")

ggplot(counts, aes(cyl, n, fill = cyl)) +
  geom_col(width = 0.72, color = "white") +
  albersdown::scale_fill_albers(family = params$family) +
  labs(
    title = "Cylinder counts",
    subtitle = "Fill accents should move to ochre while layout keeps the structural preset",
    x = "Cylinders",
    y = "Count",
    fill = "Cylinders"
  )
```

## Table Evidence

```{r}
knitr::kable(
  aggregate(cbind(mpg, wt, hp) ~ cyl, data = mtcars, FUN = mean),
  digits = 1,
  caption = "Grouped summary to inspect borders, spacing, and the overall preset mood."
)
```

```{r cleanup, include=FALSE}
options(oldopt)
if (exists("oldtheme")) ggplot2::theme_set(oldtheme)
```
