---
title: 'Theme Proof: Teal + Study'
name: proof-teal-study
description: Full-page proof vignette for the teal family on the study preset.
output:
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 2
    css: albers.css
    includes:
      in_header: albers-header.html
params:
  family: teal
  preset: study
  base_size: 13
  content_width: 78
  style: assertive
vignette: |
  %\VignetteIndexEntry{Theme Proof: Teal + Study}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
resource_files:
- albers.css
- albers.js
- albers-header.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.align = "center", fig.retina = 2,
  out.width = "100%", fig.width = 7, fig.asp = 0.618, message = FALSE, warning = FALSE
)
set.seed(7)
oldopt <- options(pillar.sigfig = 7, width = 80)
`%||%` <- function(a, b) if (is.null(a)) b else a
library(ggplot2)
if (requireNamespace("ggplot2", quietly = TRUE) && requireNamespace("albersdown", quietly = TRUE)) {
  oldtheme <- ggplot2::theme_set(albersdown::theme_albers(
    family = params$family,
    preset = params$preset,
    base_size = params$base_size
  ))
}
```

```{r albers-family, echo=FALSE, results='asis'}
cat(sprintf('<script>document.addEventListener("DOMContentLoaded",function(){document.body.classList.add("palette-%s");});</script>', params$family))
```

```{r albers-preset, echo=FALSE, results='asis'}
cat(sprintf('<script>document.addEventListener("DOMContentLoaded",function(){document.body.classList.add("preset-%s");});</script>', params$preset))
```

```{r albers-style, echo=FALSE, results='asis'}
style_class <- switch(
  tolower(params$style %||% "balanced"),
  minimal = "style-minimal",
  assertive = "style-assertive",
  balanced = ""
)
if (nzchar(style_class)) {
  cat(sprintf('<script>document.addEventListener("DOMContentLoaded",function(){document.body.classList.remove("style-minimal","style-assertive");document.body.classList.add("%s");});</script>', style_class))
}
```

```{r content-width, echo=FALSE, results='asis'}
cat(sprintf('<style>:root{--content:%sch}</style>', params$content_width))
```

<div class="albers-plate" aria-hidden="true">
  <div class="albers-plate__outer"></div>
  <div class="albers-plate__inner"></div>
  <div class="albers-plate__core"></div>
</div>

## Why This Page Exists

This page is a direct proof vignette: it fixes the family at `teal` and the preset at `study`
so readers can inspect a full article instead of a matrix or control panel.

The accent should read as teal in links, rules, callouts, and plotted highlights.
For a quick contrast check, compare this page against [pkgdown](https://pkgdown.r-lib.org/).

> The point is not variety inside one page. The point is one stable combination rendered end to end.

## Palette Evidence

```{r}
albersdown::albers_swatch(families = params$family, show_presets = TRUE) +
  ggplot2::labs(
    title = "Teal palette tones with preset row",
    subtitle = "The page family is fixed to teal so CSS and ggplot accents should agree"
  ) +
  ggplot2::theme(legend.position = "none")
```

## Plot Evidence

```{r}
mtcars |>
  transform(cyl = factor(cyl)) |>
  ggplot(aes(wt, mpg, color = cyl)) +
  geom_point(size = 2.6, alpha = 0.9) +
  geom_smooth(se = FALSE, linewidth = 0.8) +
  albersdown::scale_color_albers(family = params$family) +
  labs(
    title = "Fuel efficiency vs. weight",
    subtitle = "Legend accents and annotation ink should stay in the teal family",
    x = "Weight (1000 lbs)",
    y = "Miles per gallon",
    color = "Cylinders"
  )
```

## Table Evidence

```{r}
knitr::kable(
  head(mtcars[, c("mpg", "wt", "hp", "qsec")], 6),
  digits = 1,
  caption = "A simple table to inspect rules, spacing, and code-adjacent typography."
)
```

```{r cleanup, include=FALSE}
options(oldopt)
if (exists("oldtheme")) ggplot2::theme_set(oldtheme)
```
