---
title: 'Theme Proof: Homage + Teal'
name: proof-teal-study
description: A full page in the warm Homage direction with the teal family.
output:
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 2
    css: albers.css
    includes:
      in_header: albers-header.html
params:
  family: teal
  preset: homage
  base_size: 13
  content_width: 78
  style: minimal
resource_files:
- albers.css
- albers.js
- albers-header.html

vignette: |
  %\VignetteIndexEntry{Theme Proof: Homage + Teal}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.align = "center", fig.retina = 2,
  out.width = "100%", fig.width = 7, fig.asp = 0.6, message = FALSE, warning = FALSE
)
set.seed(123)
library(ggplot2)
if (requireNamespace("ragg", quietly = TRUE)) knitr::opts_chunk$set(dev = "ragg_png")
if (requireNamespace("systemfonts", quietly = TRUE)) albersdown::albers_register_fonts()
if (requireNamespace("ggplot2", quietly = TRUE) && requireNamespace("albersdown", quietly = TRUE)) {
  ggplot2::theme_set(albersdown::theme_albers(family = params$family, preset = params$preset))
}
```

```{r albers-classes, echo=FALSE, results='asis'}
cat(sprintf(
  paste0(
    '<script>document.addEventListener("DOMContentLoaded",function(){',
    'document.body.classList.remove("palette-red","palette-lapis","palette-ochre","palette-teal","palette-green","palette-violet","preset-homage","preset-interaction","preset-study","preset-structural","preset-adobe","preset-midnight");',
    'document.body.classList.add("palette-%s","preset-%s");',
    '});</script>'
  ),
  params$family,
  params$preset
))
```

## What this page proves

This is a full page in the **Homage** direction (warm cream ground, Newsreader
serif body, light code) with the **teal** family. The accents — links, the
nested-square marker, the code rule, and the plot palette — all shift to teal
while the warm ground and serif type stay put. Compare it against
`vignette("getting-started")` (homage + red) to see the family swap in isolation.

> TIP: A direction and a family are independent. Keep the direction for mood,
> change the family for accent character.

## Code on a light ground

```{r}
albersdown::albers_palette("teal")
```

Inline tokens like `theme_albers()` and `scale_color_albers()` stay legible
against the warm surface.

## A table

```{r}
knitr::kable(
  head(mtcars[, c("mpg", "wt", "hp", "cyl")]),
  caption = "Teal accents on the table header rule."
)
```

## A plot on the matching ground

```{r}
ggplot(mtcars, aes(wt, mpg, colour = factor(cyl))) +
  geom_point(size = 2.3) +
  albersdown::scale_color_albers(family = params$family) +
  labs(
    title = "Fuel efficiency vs. weight",
    subtitle = "Homage ground with teal accents",
    x = "Weight (1000 lbs)", y = "MPG", colour = "Cylinders"
  )
```
