---
title: "Albers components"
name: components
description: "A quick tour of the Albers cues: anchors, hero, callouts, code copy, plots, fills, and gt."
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
params:
  family: "violet"
  base_size: 14
  content_width: 72
vignette: >
  %\VignetteIndexEntry{Albers components}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
css: albers.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.align = "center", fig.retina = 2,
  out.width = "100%", fig.width = 7, fig.asp = 0.618, message = FALSE, warning = FALSE
)
set.seed(1); options(pillar.sigfig = 7, width = 80)
library(ggplot2)
if (requireNamespace("albersdown", quietly = TRUE)) {
  theme_set(albersdown::theme_albers(params$family, base_size = params$base_size))
}
```

```{r albers-family, echo=FALSE, results='asis'}
cat(sprintf('<script>document.addEventListener("DOMContentLoaded",function(){document.body.classList.add("palette-%s");});</script>', params$family))
```

```{r content-width, echo=FALSE, results='asis'}
cat(sprintf('<style>:root{--content:%sch}</style>', params$content_width))
```

```{r anchors, echo=FALSE, results='asis'}
cat('<script>document.addEventListener("DOMContentLoaded",function(){document.querySelectorAll("h2, h3").forEach(function(h){if(!h.id)return;if(h.querySelector("a.anchor"))return;var a=document.createElement("a");a.href="#"+h.id;a.className="anchor";a.textContent="—";a.setAttribute("aria-label","Link to this section");a.setAttribute("title","Link to this section");h.appendChild(a);});});</script>')
```

<div class="homage-hero--letterbox" aria-hidden="true"></div>
<div class="hr-notch" role="presentation"></div>

## Anchors, links, and callouts {#anchors}

Dash anchors appear on hover/focus at the right edge of H2/H3. Links use the family’s AA tone (e.g., [pkgdown docs](https://pkgdown.r-lib.org/)).

> TIP: Keep callouts crisp; the A300 tint stays at ≈8%.

## Copyable code and long lines {#code}

```r
long_vector <- paste(rep("abcdef", 20), collapse = ":")
long_vector
```

## Color scales (lines/points) {#color}

```{r}
mtcars$grp <- factor(ifelse(mtcars$cyl == 6, "highlight", "other"), levels = c("other", "highlight"))
ggplot(mtcars, aes(wt, mpg, color = grp)) +
  geom_point(size = 2.2) +
  albersdown::scale_color_albers_highlight(family = params$family, tone = "A700") +
  labs(title = "Highlight vs other (color)", subtitle = "A700 highlights; gray recedes")
```

## Fill scales (bars/histograms) {#fill}

```{r}
mtcars$grp2 <- factor(ifelse(mtcars$mpg > 25, "highlight", "other"), levels = c("other", "highlight"))
ggplot(mtcars, aes(grp2, fill = grp2)) +
  geom_bar(width = 0.7) +
  albersdown::scale_fill_albers_highlight(family = params$family, tone = "A700") +
  guides(fill = "none") +
  labs(title = "Highlight vs other (fill)")
```

## gt tables {#gt}

```{r}
if (requireNamespace("gt", quietly = TRUE)) {
  head(mtcars[, 1:5], 6) |>
    gt::gt() |>
    albersdown::gt_albers(family = params$family)
}
```

## See also {#see-also}

<div class="hr-notch" role="presentation"></div>

- Getting started: `articles/getting-started.html`
- Design notes: `articles/design-notes.html`
- pkgdown docs: https://pkgdown.r-lib.org/
