---
title: "Albersdown Demo"
name: getting-started
description: "A quiet, minimalist vignette styled with Albers."
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    css: albers.css
    includes:
      in_header: albers-header.html
params:
  family: "green"
  base_size: 14
  content_width: 72
vignette: >
  %\VignetteIndexEntry{Albersdown Demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
resource_files:
  - albers.css
  - albers.js
  - albers-header.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.align = "center", fig.retina = 2,
  out.width = "100%", fig.width = 7, fig.asp = 0.618, message = FALSE, warning = FALSE
)
set.seed(123); options(pillar.sigfig = 7, width = 80)
library(ggplot2)
if (requireNamespace("albersdown", quietly = TRUE)) {
  theme_set(albersdown::theme_albers(params$family, base_size = params$base_size))
}
```

```{r albers-family, echo=FALSE, results='asis'}
cat(sprintf('<script>document.addEventListener("DOMContentLoaded",function(){document.body.classList.add("palette-%s");});</script>', params$family))
```

<div class="homage-hero" aria-hidden="true"></div>
<div class="hr-notch" role="presentation"></div>

```{r content-width, echo=FALSE, results='asis'}
cat(sprintf('<style>:root{--content:%sch}</style>', params$content_width))
```

```{r anchors, echo=FALSE, results='asis'}
cat('<script>document.addEventListener("DOMContentLoaded",function(){document.querySelectorAll("h2, h3").forEach(function(h){if(!h.id)return;if(h.querySelector("a.anchor"))return;var a=document.createElement("a");a.href="#"+h.id;a.className="anchor";a.textContent="—";a.setAttribute("aria-label","Link to this section");a.setAttribute("title","Link to this section");h.appendChild(a);});});</script>')
```

## Goal

This vignette demonstrates the `albersdown` vignette look and feel.

> TIP: Keep paragraphs short; let code and output carry the meaning.

## Overview {.overview}

- One family per page (here: `{params$family}`)
- Links and focus use the family’s AA tone (e.g., [a visible link](https://pkgdown.r-lib.org/))
- Callouts, code, tables, and dash anchors show the Albers cues

## TL;DR {#tldr}

```{r}
summary(mtcars$mpg)
```

## A small plot {#plot}

```{r}
mtcars |>
  ggplot(aes(wt, mpg, color = factor(cyl))) +
  geom_point(size = 2.2) +
  albersdown::scale_color_albers(params$family, discrete = TRUE) +
  labs(title = "Fuel efficiency vs. weight",
       subtitle = "Example with Albers theme", x = "Weight (1000 lbs)", y = "MPG")
```

## A small table {#table}

```{r}
knitr::kable(head(mtcars[, 1:5], 5))
```

## A gt table with Albers styling {#gt-table}

```{r}
if (requireNamespace("gt", quietly = TRUE)) {
  head(mtcars[, 1:5], 6) |>
    gt::gt() |>
    albersdown::gt_albers(family = params$family)
} else {
  knitr::kable(head(mtcars[, 1:5], 6))
}
```

## See also {#see-also}

<div class="hr-notch" role="presentation"></div>

- Internal anchor example: [The plot](#plot)
- pkgdown docs: https://pkgdown.r-lib.org/
- Homage design notes: ../design-notes.html

```{r albers-family, echo=FALSE, results='asis'}
cat(sprintf('<script>document.addEventListener("DOMContentLoaded",function(){document.body.classList.add("palette-%s");});</script>', params$family))
```
