---
title: 'Theme Proof: Homage + Teal'
name: proof-teal-study
description: A full page in the warm Homage direction with the teal family.
output:
  albersdown::albers_vignette:
    family: teal
    preset: homage
    toc: yes
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.align = "center", fig.retina = 2,
  out.width = "100%", fig.width = 7, fig.asp = 0.6, message = FALSE, warning = FALSE
)
set.seed(123)
library(ggplot2)
```

## What this page proves

This is a full page in the **Homage** direction (warm cream ground, Newsreader
serif body, light code) with the **teal** family. The accents — links, the
nested-square marker, the code rule, and the plot palette — all shift to teal
while the warm ground and serif type stay put. Compare it against
`vignette("getting-started")` (homage + red) to see the family swap in isolation.

> TIP: A direction and a family are independent. Keep the direction for mood,
> change the family for accent character.

## Code on a light ground

```{r}
albersdown::albers_palette("teal")
```

Inline tokens like `theme_albers()` and `scale_color_albers()` stay legible
against the warm surface.

## A table

```{r}
knitr::kable(
  head(mtcars[, c("mpg", "wt", "hp", "cyl")]),
  caption = "Teal accents on the table header rule."
)
```

## A plot on the matching ground

```{r}
ggplot(mtcars, aes(wt, mpg, colour = factor(cyl))) +
  geom_point(size = 2.3) +
  albersdown::scale_color_albers() +
  labs(
    title = "Fuel efficiency vs. weight",
    subtitle = "Homage ground with teal accents",
    x = "Weight (1000 lbs)", y = "MPG", colour = "Cylinders"
  )
```
