---
title: 'Theme Proof: Interaction + Ochre'
name: proof-ochre-structural
description: A full page in the cool Interaction direction with the ochre family.
output:
  albersdown::albers_vignette:
    family: ochre
    preset: interaction
    toc: yes
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.align = "center", fig.retina = 2,
  out.width = "100%", fig.width = 7, fig.asp = 0.6, message = FALSE, warning = FALSE
)
set.seed(123)
library(ggplot2)
```

## What this page proves

This is a full page in the **Interaction** direction (cool grey ground, grotesk
type, dark code blocks) with the **ochre** family. The same dark code panel and
cool ground as `vignette("interaction")`, but the accents — links, the
nested-square marker, the syntax-accent rule, and the plot palette — are ochre
rather than lapis. Direction sets the mood; family sets the hue.

> TIP: On the dark code ground, the syntax token colours adapt automatically so
> code stays legible regardless of the family.

## Code on a dark ground

```{r}
albersdown::albers_palette("ochre")
```

Inline code such as `theme_albers(preset = "interaction")` stays a light chip so
it reads inside the body text.

## A table

```{r}
knitr::kable(
  head(mtcars[, c("mpg", "wt", "hp", "cyl")]),
  caption = "Ochre accents on the table header rule, cool ground."
)
```

## A plot on the matching ground

```{r}
ggplot(mtcars, aes(wt, mpg, colour = factor(cyl))) +
  geom_point(size = 2.3) +
  albersdown::scale_color_albers() +
  labs(
    title = "Fuel efficiency vs. weight",
    subtitle = "Interaction ground with ochre accents",
    x = "Weight (1000 lbs)", y = "MPG", colour = "Cylinders"
  )
```
