---
title: 'Theme Lab: Tune Family, Preset, and Rhythm'
name: theme-lab
description: Interactive controls for palette family, direction, style intensity,
  and reading width.
output:
  albersdown::albers_vignette:
    fonts: both
    family: red
    preset: homage
    toc: yes
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.align = "center", fig.retina = 2,
  out.width = "100%", fig.width = 7, fig.asp = 0.618, message = FALSE, warning = FALSE
)
library(ggplot2)
```

## What Is This Page For?

Use this page to choose a visual direction before you retrofit or create vignettes.
You can tune one parameter at a time and immediately see the effect on hierarchy,
contrast, and page rhythm.

<div class="callout callout-insight">
Start with <strong>family</strong> and <strong>preset</strong>, then tune <strong>style</strong>, then adjust content width.
That order gives the fastest path to a coherent page.
</div>

## How Do You Use It?

1. Pick a family for color character (the four chips show its tones).
2. Pick a direction: warm **homage** or cool **interaction**.
3. Toggle style intensity to set structural emphasis (marker + rule weight).
4. Adjust content width to match prose density.

<div class="theme-lab" data-albers-lab>
<div class="theme-lab__panel">
  <div class="theme-lab__controls">
  <div>
  <label for="albers-family">Family</label>
  <select id="albers-family" data-albers-control="family">
  <option value="red">red</option>
  <option value="lapis">lapis</option>
  <option value="ochre">ochre</option>
  <option value="teal">teal</option>
  <option value="green">green</option>
  <option value="violet">violet</option>
  </select>
  </div>
  <div>
  <label for="albers-preset">Direction</label>
  <select id="albers-preset" data-albers-control="preset">
  <option value="homage">homage (warm)</option>
  <option value="interaction">interaction (cool)</option>
  </select>
  </div>
  <div>
  <label for="albers-style">Style</label>
  <select id="albers-style" data-albers-control="style">
  <option value="minimal">minimal</option>
  <option value="balanced">balanced</option>
  <option value="assertive">assertive</option>
  </select>
  </div>
  <div>
  <label for="albers-width">Content width (ch)</label>
  <input id="albers-width" data-albers-control="width" type="number" min="56" max="100" placeholder="66" />
  </div>
  </div>
</div>

<div class="theme-lab__preview">
  <div class="theme-lab__chips">
  <span class="albers-chip">A900</span>
  <span class="albers-chip">A700</span>
  <span class="albers-chip">A500</span>
  <span class="albers-chip">A300</span>
  </div>
  <p data-albers-lab-summary>family=red | preset=homage | style=minimal | width=66ch</p>
  <div class="albers-composition albers-composition--dense" data-seed="theme-lab" data-density="8" aria-hidden="true"></div>
</div>
</div>

## What Does Each Control Change?

- `family`: accent hue and contrast character for links, rules, the nested-square
  marker, and plot palettes (the four chips above show the active family's tones).
- `preset` (direction): warm **homage** (cream ground, serif body, light code) vs
  cool **interaction** (grey ground, grotesk, dark code).
- `style`: structural weight (`minimal` or `assertive`).
- Content width: the reading measure in `ch` units, for this preview only. The
  theme sets it (66ch in homage, 64ch in interaction); it is not a format
  option.

## Can You Validate The Palette Quickly?

```{r palette-check}
# the format sets the albersdown.family option to the vignette's family
pal <- albersdown::albers_palette(getOption("albersdown.family", "red"))
stopifnot(
  identical(names(pal), c("A900", "A700", "A500", "A300")),
  all(nzchar(unname(pal)))
)
knitr::kable(data.frame(tone = names(pal), hex = unname(pal)), format = "html")
```

## Copy Into YAML

Put the choice in the vignette's output format:

```{.yaml #albers-lab-yaml}
output:
  albersdown::albers_vignette:
    family: red        # red, lapis, ochre, teal, green, violet
    preset: homage     # homage or interaction
    style: minimal     # minimal, balanced or assertive
```

## Example Plot

```{r example-plot}
mtcars$grp <- factor(mtcars$cyl)
stopifnot(length(levels(mtcars$grp)) >= 3)

ggplot(mtcars, aes(wt, mpg, colour = grp)) +
  geom_point(size = 2.2) +
  albersdown::scale_color_albers() +
  labs(
    title = "Theme Lab preview",
    subtitle = "Tune family + preset + style, then copy YAML"
  )
```
